Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-30 ms.tex
Added some boldface and additional edits to text.  Last bit is to address the HST PSF

\documentclass{emulateapj}
\usepackage{amsmath} 
\usepackage{apjfonts} 
\usepackage{amssymb} 
\usepackage{xspace}
\usepackage{hyperref} 
\usepackage{natbib} 
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsf}
\usepackage{subfigure}
\bibliographystyle{apj_ads}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\comment}[1]{{\color{red} #1}}
\newcommand{\wording}[1]{{\it\color{purple} #1}}
\newcommand{\todo}[1]{{\bf\color{blue} #1}}
%%%%%%%%%% User defined symbol %%%%%%
\def\gsim{\gtrsim}
\def\lsim{\lesssim}    
\def\Msun{M_\odot}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%-------------------------------------------------%
\begin{abstract} 
Gravitational lensing offers a direct probe of the underlying mass
distribution of lensing systems, a window to the high redshift
universe, and a geometric probe of cosmological models.  The advent of
large scale surveys such as the Large Synoptic Sky Telescope and
Euclid has prompted a need for automatic and efficient identification
of strong lensing systems.  We present (1) {\em (ALL) Automated
  Lensing Learner}, a strong lensing identification pipeline that will
be publicly released as open source software, and (2) a publicly
available mock LSST dataset with strong galaxy-galaxy lenses.  In this
first application of the pipeline, we employ a fast feature extraction
method, Histogram of Oriented Gradients (HOG), to capture edge
patterns that are characteristic of strong gravitational arcs in
galaxy-galaxy lensing.  We use logistic regression to train a
supervised classifier model on the HOG of HST- and LSST-like images.
We use the area under the curve (AUC) of a Receiver Operating
Characteristic (ROC) curve to assess model performance; $AUC=1.0$ is an
ideal classifier, and $AUC=0.5$ is no better than randomly guessing.
Our best performing models on a training
set of 10,000 lens containing images and 10,000 non-lens containing
images exhibit an AUC of 0.975 for an HST-like sample.  However, for
one exposure of LSST, our model only reaches an AUC of 0.625.  For
10-year mock LSST observations, the AUC improves to 0.809.  Model
performance appears to continually improve with the size of the
training set.  Models trained on fewer images perform better in
absence of the lens galaxy, the removal of which can decrease the
false positive rate due to the blending of light between source images
and the lens galaxy.  However, with larger training data sets,
information from the lens galaxy actually improves model performance.
Our results demonstrate an efficient and effective method for automatically
identifying strong lenses that captures much of the complexity of the
arc finding problem. The linear classifier both runs on a
personal laptop and can easily scale to large data sets on a computing
cluster, all while using existing open source tools.
\end{abstract}
%-------------------------------------------------%

@@

% Gravitational lensing as a geometric test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.
Gravitational lensing occurs when intermediate fluctuations in the
matter density field deflect light from background sources
\citep[see][for a review]{kneibandnatarajan_11}.  Strong gravitational
lensing can manifest as visible giant arcs magnifying high redshift
galaxies \citep{lyndsandpetrosian_86,gladders_etal03}, multiply imaged
quasars \citep{walsh_etal79}, multiply imaged galaxies
\citep{sharon_etal05}, and arclets \citep{bezecourt_etal98}.  Lensing
signatures probe the underlying dark matter distribution of the lens
\citep{warrenanddye_03}, and high redshift galaxy formation
\citep{allam_etal07}. Strong lenses also provide a geometric test of
cosmology via comparison of predicted arc abundances with observed
abundances \citep{kochanek_96,chae_03,linder_04}, via time-delay
between signals from multiply imaged quasars
\citep{xli_etal12,suyu_etal14,suyu_etal16,bonvin_etal17}, and via
distance ratios in lenses with sources at multiple redshifts
\citep{jullo_etal10,collett_etal12,collettandauger_14}.

% Application of constraining mass profiles - large numbers needed.
The application of strong gravitational lensing to constrain the mass
distribution of strong lenses, such as early-type galaxies (ETGs),
necessitates large samples of galaxy-galaxy lensing systems.
\citet{miraldaescudeandlehar_92} first suggested that massive
ellipticals would likely be frequent strong lensing sources in optical
surveys.  These systems contain a background source galaxy that the
lens galaxy deflects into a partial or full arc shaped Einstein ring.
The strong lensing signature directly probes the underlying matter.
The identification of such systems in upcoming surveys is the first
step in constraining the mass-to-light ratio for a large number of
objects in this mass range.

% Image identification works: visual, ``robot'' identification -
% ArcFinder, RingFinder..., and citizen science (space warps).  Many
% of these rely on some explicit aspect of the image's morphology
% (give example), filtering, ... ....  Specifics of the methodology
% how the instrument affects the strong lensing signal, and the
% objects of interest.
Over the last decade, infrastructure for both large scale visual and
automated image classification emerged. By nature, the human eye is
one of the best discriminators for image classification.  Visual arc
identification has been effective through the use of citizen science
platforms.  {\em SpaceWarps} is an example of citizen science based
image classification of strong lensing systems in Canada France Hawaii
Telescope Science (CFHTLS) telescope observations
\citep{marshall_etal16,more_etal16}.  These platforms are quite
successful for a dataset like CFHTLS; here, 3,000 candidate images
were identified in eight months, resulting in 89 final candidates.
However, future datasets like Euclid \citep{oguriandmarshall_10} and
LSST expect to find hundreds of thousands galaxy-scale strong lenses
\citep{collett_15}.  The volume of upcoming data challenges the
scalability of a pure citizen science approach.

@@

Mock observations of lensing systems include the lens galaxy, lensed
images of the source galaxy, and galaxies along the line of sight.
Mock observations of non-lensing systems include all but the images of
a lensed source galaxy.  We convolve each of the $2\times 10,000$
train/test images and $2\times 1,000$ hold-out images to produce three
separate sets of mock ``observations''.  These each have equal numbers
of lens and non-lens containing systems: (1) HST-like observations,
(2) best single exposure LSST-like observations, and (3) LSST-like
observations over the span of ten years.  We respectively label these
observations as HST, LSST-best, and LSST10.

@@

The normalized convergence map of the SIE model is defined as:
%-------------------------------------------------%
\begin{equation}\label{eqn:sie}
\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}},
\end{equation}
%-------------------------------------------------%
where $\theta_{\rm E}$ is the Einstein Radius and $q$ is the axis ratio.
The Einstein radius can be calculated from the redshift of the
lens, the redshift of the source, and the velocity dispersion of the
lens galaxy as follows,
%-------------------------------------------------%
\begin{equation}
\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}, 
\end{equation}
%-------------------------------------------------%
Here, $c$ is the speed of light, $\sigma_v$ is the velocity dispersion
of the lens galaxy, $D_{ls}$ and $D_{s}$ are respectively the angular
diameter distances from the source plane to the lens plane and from
the source plane to the observer.

@@

We choose $\sigma_v$, $q$, and $\phi$ randomly from typical ranges of
observed galaxies: $\sigma_v \in [200, 320]~km/s$, $q \in [0.5, 1.0]$,
and $\phi \in [0, 360]$.  We obtain the redshift of the lens galaxy by
matching the velocity dispersion from our simulations to the catalog
of elliptical galaxies in the COSMOS survey from \citet{zahid_etal15},
resulting in lens galaxy redshifts in the range, $z_l \in [0.2,0.7]$.

@@

%-------------------------------------------------%
\subsubsection{Modeling Images of the Source Galaxies}
%-------------------------------------------------%
The background source galaxies come from a set of detailed images of
low-redshift bright galaxies ($z\sim0.45$) that have been extracted
from mosaics produced by the CANDELS team
\citep{grogin_etal11,koekemoer_etal11} and selected from the CANDELS
UDS catalog \citep{galametz_etal13}.  We rescale these background
source galaxies, set the source redshift to $z_s=0.2$, and select
source positions near caustics of the lensing system.  We then fix the
projected position of the lens galaxy at the center of the field of
view for each image.

@@

The final part is to perform the mock observation from the ideal
images produced in the previous step. For HST-like observations,
galaxies along the line of sight already include noise and a point
spread function (PSF).  We therefore stack and magnitude calibrate all
components to produce the final HST-like images, which are
$300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.

@@

To account for variations in seeing and sky-brightness over the course
of the survey, we draw each simulated exposure from a stochastic
distribution of these parameters. We then consider two different
strategies to use the simulated exposures. First, we build one
single-epoch image for each field (hereafter labeled as LSST-best) by
keeping only the best seeing exposure.  Second, we build another
``worst-case'' stacked image by degrading all individual exposures,
ten per filter per year, to match the one with the worst seeing and
co-add all exposures to a single image (hereafter labeled as LSST10).
These two sets of images will allow us to investigate the trade-off
between resolution and signal-to-noise for our automated lens search.

@@

The middle column corresponds to the same simulated systems for
LSST10.  The right-most column corresponds to the simulated systems of
LSST-best.  These images have resolution $45\times45~{\rm pixels}^2$ with
$0.18$~arcsec/pixel.  LSST10 images visually exhibit the improved
signal to noise ratio, recovering the arc feature, albeit at a much
lower resolution than with the HST-like image or the LSST-best image.
The top images of LSST10 and LSST-best show a visible lensed source
galaxy image.  The bottom images are washed out in the bottom row,
where the magnification of the source galaxy is not as large.  The
ground based noise, PSF, and limited resolution of the LSST-best make
visual giant arc identification difficult, except in systems with the
most magnified source galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{figures/tiles/compilations/telescope_compilation.pdf}
\caption{Left to right show example mock HST, LSST 10 year, and
  LSST-best images.  The top row corresponds to a lensing system with a
  very visible arc signature, and the bottom row to a lensing system
  that is less obvious.  Example mock HST images have
  $n_\text{pix}\times n_\text{pix}=300\times300$.  Example mock LSST
  images have $n_\text{pix}\times n_\text{pix}=45\times45$.  The
  resolution and noise of a ground based telescope is noticeably
  worse. Visual identification of giant arcs in the LSST images in the
  bottom row is very difficult.}\label{fig:mockimages}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Furthermore, we investigate the influence of light from the lens
galaxies on the performance of our lens identification pipeline.  We
generate another set of each HST, LSST-best, and LSST10 images without the
lens galaxy.  We respectively label these nHST, nLSST-best, and nLSST10.

@@

Finally, the resolution of the overall image will also limit the
additional information that an increase in $N_\text{orient}$ will
provide.  From the grid search, the best case number of orientations
for each dataset is $N_\text{orient,HST}=9$,
$N_\text{orient,LSST10}=3$, and $N_\text{orient,LSST-best}=5$.

@@

% Summary of ROC curves
Figure~\ref{fig:ROCcompilation} shows the ROC curves for models
trained using the entire 10,000 training sample, with best-case HOG
and regularization parameters.  The models have been evaluated on a
hold-out set of 1,000 images that were not used in the parameter
search.  We show the mock HST, LSST-best, and LSST10 results respectively
in red, blue, and green.  Solid lines correspond to a model trained
and tested on images with the lensing galaxy.  Dashed lines correspond
to a model trained and tested on images where the lensing galaxy is
excluded from the mock observation, simulating an ideal modeling and
subtraction of the lensing galaxy, which has been one proposed method
to improve the identification of strong lensing systems.  The
corresponding AUC is listed in the legend.

@@

%  Our running over C - score and AUC as characterizations
Figure~\ref{fig:regularization} shows the model performance as a
function of regularization parameter for each data set HST, LSST-best, and
LSST10.  The solid and dotted blue lines respectively correspond to
the model performance on the test and training set, with the AUC as a
metric for performance.  In red, we show the train time as a function
of $C_{LogReg}$.

@@

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
\begin{center}
\includegraphics[width=.66\columnwidth]{figures/Creg/HST.pdf}
\includegraphics[width=.66\columnwidth]{figures/Creg/LSST1.pdf}
\includegraphics[width=.66\columnwidth]{figures/Creg/LSST10.pdf}
\caption{AUC of the model with varying LR regularization coefficient
  parameter, $C_{LogReg}$, used when training the model classifier.  We
  use a subset of the 10,000 training images to search over the LR
  $C_{LogReg}$ parameter, training on 8,000 and testing on 1,000.  Each
  panel corresponds to a different mock observation.  From left to
  right: HST, LSST for one year, and LSST for 10 years.  The solid
  blue lines correspond to the AUC of the test set, and the dotted
  blue lines to the AUC of the training set.  To avoid overfitting, we
  choose the smallest parameter for which the AUC of the test set is
  maximal: 5000, 10, and 5000, respectively.  In thin red solid lines,
  we show the train time of the model, which roughly increases in a
  log-log scaling with logistic regression coefficient
  parameter.}\label{fig:regularization}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% LSST10 and nLSST10 behavior
Figure~\ref{fig:trainsizeLSST} shows how the AUC depends on the log of
the size of the training set for both the LSST10 (LSST-best) data in the
solid blue (red) line, and the nLSST10 (nLSST-best) data in dashed blue
(red) line.  The AUC for models trained on the LSST10 data improves
almost linearly with the log of the training set size, increasing from
AUC=0.705 to AUC=0.788 when the train size is increased from
$2\times500$ lens/non-lens images to $2\times8000$ lens/non-lens
images.  However, for the nLSST10 data, where the lens galaxy has been
removed from the images, the improvement is less dramatic.  With the
same increase in training size, the AUC for nLSST10 changes from just
below 0.77 to just below 0.78.

@@

% LSST1 and nLSST1 behavior
In red, we see an analogous improvement for LSST-best and nLSST-best.
Here, the crossover happens at train size of $2x1000$, where an
increase in larger training data set size does not help improve the
AUC for nLSST-best.

@@

% Train time behavior for LSST1 and nLSST1
For LSST-best, Figure~\ref{fig:traintimeLSST1} shows the same
relationships between train time and train size in blue, and the
optimal regulariztion parameter (or model complexity) in red.
Contrary to what we found when comparing LSST10 to nLSST10, nLSST-best
requires more model complexity than LSST-best.  Recall that LSST-best and
nLSST-best correspond to single epoch simulated exposures with the best
seeing; these images exhibit better resolution but worse signal to
noise.  The switch in required model complexity corresponds to a
trade-off between features from the lens galaxy providing additional
information or swamping the signal from a strong lensing arc.

% AUC vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/trainsize/combined_LSST10_with_nLSST10.pdf}
\caption{Solid (dotted) blue line: AUC for models with varying size of
  the training set for LSST10 (nLSST10).  Solid (dotted) red line:
  Same for LSST-best. The improvement of AUC scales roughly linearly with
  the log of the training set size.  However, LSST10 and LSST-best have a
  steeper improvement with data training size.  The performance of
  nLSST10 and nLSST-best models trained on smaller training data sets is
  better than the respective LSST10 and LSST-best models trained on the
  same size data, but the LSST10 and LSST-best models outperform with
  larger size training data set.}\label{fig:trainsizeLSST}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass{emulateapj}
\usepackage{amsmath} 
\usepackage{apjfonts} 
\usepackage{amssymb} 
\usepackage{xspace}
\usepackage{hyperref} 
\usepackage{natbib} 
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsf}
\usepackage{subfigure}
\bibliographystyle{apj_ads}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\comment}[1]{{\color{red} #1}}
\newcommand{\wording}[1]{{\it\color{purple} #1}}
\newcommand{\todo}[1]{{\bf\color{blue} #1}}
\newcommand{\edit}[1]{{\bf #1}}
%%%%%%%%%% User defined symbol %%%%%%
\def\gsim{\gtrsim}
\def\lsim{\lesssim}    
\def\Msun{M_\odot}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%-------------------------------------------------%
\begin{abstract} 
Gravitational lensing offers a direct probe of the underlying mass
distribution of lensing systems, a window to the high redshift
universe, and a geometric probe of cosmological models.  The advent of
large scale surveys such as the Large Synoptic Sky Telescope and
Euclid has prompted a need for automatic and efficient identification
of strong lensing systems.  We present (1) {\em (ALL) Automated
  Lensing Learner}, a strong lensing identification pipeline that will
be publicly released as open source software, and (2) a publicly
available mock LSST dataset with strong galaxy-galaxy lenses.  In this
first application of the pipeline, we employ a fast feature extraction
method, Histogram of Oriented Gradients (HOG), to capture edge
patterns that are characteristic of strong gravitational arcs in
galaxy-galaxy \edit{strong} lensing.  We use logistic regression to train a
supervised classifier model on the HOG of HST- and LSST-like images.
We use the area under the curve (AUC) of a Receiver Operating
Characteristic (ROC) curve to assess model performance; $AUC=1.0$ is an
ideal classifier, and $AUC=0.5$ is no better than randomly guessing.
Our best performing models on a training
set of 10,000 lens containing images and 10,000 non-lens containing
images exhibit an AUC of 0.975 for an HST-like sample.  However, for
\edit{one exposure} of LSST, our model only reaches an AUC of 0.625.  For
10-year mock LSST observations, the AUC improves to 0.809.  Model
performance appears to continually improve with the size of the
training set.  Models trained on fewer images perform better in
absence of the lens galaxy, the removal of which can decrease the
false positive rate due to the blending of light between source images
and the lens galaxy.  However, with larger training data sets,
information from the lens galaxy actually improves model performance.
Our results demonstrate an efficient and effective method for automatically
identifying strong lenses that captures much of the complexity of the
arc finding problem. The linear classifier both runs on a
personal laptop and can easily scale to large data sets on a computing
cluster, all while using existing open source tools.
\end{abstract}
%-------------------------------------------------%

@@

% Gravitational lensing as a geometric test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.
Gravitational lensing occurs when intermediate fluctuations in the
matter density field deflect light from background sources
\citep[see][for a review]{kneibandnatarajan_11}.  Strong gravitational
lensing can manifest as visible giant arcs magnifying high redshift
galaxies \citep{lyndsandpetrosian_86,gladders_etal03}, multiply imaged
quasars \citep{walsh_etal79}, multiply imaged galaxies
\citep{sharon_etal05}, and arclets \citep{bezecourt_etal98}.  Lensing
signatures probe the underlying dark matter distribution of the lens
\citep{warrenanddye_03}, and high redshift galaxy formation
\citep{allam_etal07}. Strong lenses also provide a geometric test of
cosmology via comparison of predicted arc abundances with observed
abundances \citep{kochanek_96,chae_03,linder_04}, via time-delay
between signals from multiply imaged quasars \edit{
\citep{xli_etal12,suyu_etal14,suyu_etal16,bonvin_etal17}, and via
distance ratios in lenses with sources at multiple redshifts
\citep{jullo_etal10,collett_etal12,collettandauger_14}.}

% Application of constraining mass profiles - large numbers needed.
The application of strong gravitational lensing to constrain the mass
distribution of strong lenses, such as early-type galaxies (ETGs),
necessitates large samples of galaxy-galaxy \edit{strong} lensing systems.
\citet{miraldaescudeandlehar_92} first suggested that massive
ellipticals would likely be frequent strong lensing sources in optical
surveys.  These systems contain a background source galaxy that the
lens galaxy deflects into a partial or full arc shaped Einstein ring.
The strong lensing signature directly probes the underlying matter.
The identification of such systems in upcoming surveys is the first
step in constraining the mass-to-light ratio for a large number of
objects in this mass range.

% Image identification works: visual, ``robot'' identification -
% ArcFinder, RingFinder..., and citizen science (space warps).  Many
% of these rely on some explicit aspect of the image's morphology
% (give example), filtering, ... ....  Specifics of the methodology
% how the instrument affects the strong lensing signal, and the
% objects of interest.
Over the last decade, infrastructure for both large scale visual and
automated image classification emerged. By nature, the human eye is
one of the best discriminators for image classification.  Visual arc
identification has been effective through the use of citizen science
platforms.  {\em SpaceWarps} is an example of citizen science based
image classification of strong lensing systems in Canada France Hawaii
Telescope Science (CFHTLS) telescope observations
\citep{marshall_etal16,more_etal16}.  These platforms are quite
successful for a dataset like CFHTLS; here, 3,000 candidate images
were identified in eight months, resulting in 89 final candidates.
However, future datasets like Euclid \citep{oguriandmarshall_10} and
LSST expect to find \edit{hundreds of thousands galaxy-scale strong lenses
\citep{collett_15}.}  The volume of upcoming data challenges the
scalability of a pure citizen science approach.

@@

Mock observations of lensing systems include the lens galaxy, lensed
images of the source galaxy, and galaxies along the line of sight.
Mock observations of non-lensing systems include all but the images of
a lensed source galaxy.  We convolve each of the $2\times 10,000$
train/test images and $2\times 1,000$ hold-out images to produce three
separate sets of mock ``observations''.  These each have equal numbers
of lens and non-lens containing systems: (1) HST-like observations,
(2) best single exposure LSST-like observations, and (3) LSST-like
observations over the span of ten years.  We respectively label these
observations as HST, \edit{LSST-best}, and LSST10.

@@

The normalized convergence map of the SIE model is defined as:
%-------------------------------------------------%
\begin{equation}\label{eqn:sie}
\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}},
\end{equation}
%-------------------------------------------------%
where $\theta_{\rm E}$ is the Einstein Radius and $q$ is the axis ratio.
The Einstein radius can be calculated from the redshift of the
lens, the redshift of the source, and the velocity dispersion of the
lens galaxy as follows,
%-------------------------------------------------%
\begin{equation}
\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)^2\frac{D_{ls}}{D_{s}}, 
\end{equation}
%-------------------------------------------------%
Here, $c$ is the speed of light, $\sigma_v$ is the velocity dispersion
of the lens galaxy, $D_{ls}$ and $D_{s}$ are respectively the angular
diameter distances from the source plane to the lens plane and from
the source plane to the observer.

@@

We choose $\sigma_v$, $q$, and $\phi$ \edit{randomly (flat prior) from
typical ranges of observed galaxies: $\sigma_v \in [200, 320]~km/s$,
$q \in [0.5, 1.0]$, and $\phi \in [0, 360]$.  While a flat prior is
not realistic, we use this as a starting point to test our pipeline
(see Section~\ref{sec:conclusions} for more details on future
work)}. We obtain the redshift of the lens galaxy by matching the
velocity dispersion from our simulations to the catalog of elliptical
galaxies in the COSMOS survey from \citet{zahid_etal15}, resulting in
lens galaxy redshifts in the range, $z_l \in [0.2,0.7]$.

@@

%-------------------------------------------------%
\subsubsection{Modeling Images of the Source Galaxies}
%-------------------------------------------------%
The background source galaxies come from a set of detailed images of
low-redshift bright galaxies ($z\sim0.45$) that have been extracted
from mosaics produced by the CANDELS team
\citep{grogin_etal11,koekemoer_etal11} and selected from the CANDELS
UDS catalog \citep{galametz_etal13}.  We rescale these background
source galaxies, set the source redshift to \edit{$z_s=2$, and select
  source positions near caustics of the lensing system.  The selected
  positions are within a $2''\times2''$ square box centered on the
  lens galaxy center of mass.} We then fix the projected position of
the lens galaxy at the center of the field of view for each image.

@@

The final part is to perform the mock observation from the ideal
images produced in the previous step.  \edit{Both our HST- and
  LSST-like observations are monochromatic, respectively using the
  F606W and the g-band.} For HST-like observations, galaxies along the
line of sight already include noise and a point spread function (PSF).
We therefore stack and magnitude calibrate all components to produce
the final HST-like images, which are $300\times300~{\rm pix}^2$ with
$0.03$~arcsec per pixel.

@@

To account for variations in seeing and sky-brightness over the course
of the survey, we draw each simulated exposure from a stochastic
distribution of these parameters. We then consider two different
strategies to use the simulated exposures. First, we build one
single-epoch image for each field (hereafter labeled as \edit{LSST-best}) by
keeping only the best seeing exposure.  Second, we build another
``worst-case'' stacked image by degrading all individual exposures,
ten per filter per year, to match the one with the worst seeing and
co-add all exposures to a single image (hereafter labeled as LSST10).
These two sets of images will allow us to investigate the trade-off
between resolution and signal-to-noise for our automated lens search.

@@

The middle column corresponds to the same simulated systems for
LSST10.  The right-most column corresponds to the simulated systems of
\edit{LSST-best}.  These images have resolution $45\times45~{\rm pixels}^2$ with
$0.18$~arcsec/pixel.  LSST10 images visually exhibit the improved
signal to noise ratio, recovering the arc feature, albeit at a much
lower resolution than with the HST-like image or the \edit{LSST-best} image.
The top images of LSST10 and \edit{LSST-best} show a visible lensed source
galaxy image.  The bottom images are washed out in the bottom row,
where the magnification of the source galaxy is not as large.  The
ground based noise, PSF, and limited resolution of the \edit{LSST-best} make
visual giant arc identification difficult, except in systems with the
most magnified source galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{figures/tiles/compilations/telescope_compilation.pdf}
\caption{Left to right show example mock HST, LSST 10 year, and
  \edit{LSST-best} images.  The top row corresponds to a lensing system with a
  very visible arc signature, and the bottom row to a lensing system
  that is less obvious.  Example mock HST images have
  $n_\text{pix}\times n_\text{pix}=300\times300$.  Example mock LSST
  images have $n_\text{pix}\times n_\text{pix}=45\times45$.  The
  resolution and noise of a ground based telescope is noticeably
  worse. Visual identification of giant arcs in the LSST images in the
  bottom row is very difficult.}\label{fig:mockimages}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Furthermore, we investigate the influence of light from the lens
galaxies on the performance of our lens identification pipeline.  We
generate another set of each HST, \edit{LSST-best}, and LSST10 images without the
lens galaxy.  We respectively label these nHST, n\edit{LSST-best}, and nLSST10.

@@

Finally, the resolution of the overall image will also limit the
additional information that an increase in $N_\text{orient}$ will
provide.  From the grid search, the best case number of orientations
for each dataset is $N_\text{orient,HST}=9$,
$N_\text{orient,LSST10}=3$, and $N_\text{orient,\edit{LSST-best}}=5$.

@@

% Summary of ROC curves
Figure~\ref{fig:ROCcompilation} shows the ROC curves for models
trained using the entire 10,000 training sample, with best-case HOG
and regularization parameters.  The models have been evaluated on a
hold-out set of 1,000 images that were not used in the parameter
search.  We show the mock HST, \edit{LSST-best}, and LSST10 results respectively
in red, blue, and green.  Solid lines correspond to a model trained
and tested on images with the lensing galaxy.  Dashed lines correspond
to a model trained and tested on images where the lensing galaxy is
excluded from the mock observation, simulating an ideal modeling and
subtraction of the lensing galaxy, which has been one proposed method
to improve the identification of strong lensing systems.  The
corresponding AUC is listed in the legend.

@@

%  Our running over C - score and AUC as characterizations
Figure~\ref{fig:regularization} shows the model performance as a
function of regularization parameter for each data set HST, \edit{LSST-best}, and
LSST10.  The solid and dotted blue lines respectively correspond to
the model performance on the test and training set, with the AUC as a
metric for performance.  In red, we show the train time as a function
of $C_{LogReg}$.

@@

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
\begin{center}
\includegraphics[width=.66\columnwidth]{figures/Creg/HST.pdf}
\includegraphics[width=.66\columnwidth]{figures/Creg/LSST-best.pdf}
\includegraphics[width=.66\columnwidth]{figures/Creg/LSST10.pdf}
\caption{AUC of the model with varying LR regularization coefficient
  parameter, $C_{LogReg}$, used when training the model classifier.  We
  use a subset of the 10,000 training images to search over the LR
  $C_{LogReg}$ parameter, training on 8,000 and testing on 1,000.  Each
  panel corresponds to a different mock observation.  From left to
  right: HST, LSST for one year, and LSST for 10 years.  The solid
  blue lines correspond to the AUC of the test set, and the dotted
  blue lines to the AUC of the training set.  To avoid overfitting, we
  choose the smallest parameter for which the AUC of the test set is
  maximal: 5000, 10, and 5000, respectively.  In thin red solid lines,
  we show the train time of the model, which roughly increases in a
  log-log scaling with logistic regression coefficient
  parameter.}\label{fig:regularization}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% LSST10 and nLSST10 behavior
Figure~\ref{fig:trainsizeLSST} shows how the AUC depends on the log of
the size of the training set for both the LSST10 (\edit{LSST-best}) data in the
solid blue (red) line, and the nLSST10 (n\edit{LSST-best}) data in dashed blue
(red) line.  The AUC for models trained on the LSST10 data improves
almost linearly with the log of the training set size, increasing from
AUC=0.705 to AUC=0.788 when the train size is increased from
$2\times500$ lens/non-lens images to $2\times8000$ lens/non-lens
images.  However, for the nLSST10 data, where the lens galaxy has been
removed from the images, the improvement is less dramatic.  With the
same increase in training size, the AUC for nLSST10 changes from just
below 0.77 to just below 0.78.

@@

% LSST1 and nLSST1 behavior
In red, we see an analogous improvement for \edit{LSST-best} and n\edit{LSST-best}.
Here, the crossover happens at train size of $2x1000$, where an
increase in larger training data set size does not help improve the
AUC for n\edit{LSST-best}.

@@

% Train time behavior for LSST1 and nLSST1
For \edit{LSST-best}, Figure~\ref{fig:traintimeLSST1} shows the same
relationships between train time and train size in blue, and the
optimal regulariztion parameter (or model complexity) in red.
Contrary to what we found when comparing LSST10 to nLSST10, n\edit{LSST-best}
requires more model complexity than \edit{LSST-best}.  Recall that \edit{LSST-best} and
n\edit{LSST-best} correspond to single epoch simulated exposures with the best
seeing; these images exhibit better resolution but worse signal to
noise.  The switch in required model complexity corresponds to a
trade-off between features from the lens galaxy providing additional
information or swamping the signal from a strong lensing arc.

% AUC vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/trainsize/combined_LSST10_with_nLSST10.pdf}
\caption{Solid (dotted) blue line: AUC for models with varying size of
  the training set for LSST10 (nLSST10).  Solid (dotted) red line:
  Same for \edit{LSST-best}. The improvement of AUC scales roughly linearly with
  the log of the training set size.  However, LSST10 and \edit{LSST-best} have a
  steeper improvement with data training size.  The performance of
  nLSST10 and n\edit{LSST-best} models trained on smaller training data sets is
  better than the respective LSST10 and \edit{LSST-best} models trained on the
  same size data, but the LSST10 and \edit{LSST-best} models outperform with
  larger size training data set.}\label{fig:trainsizeLSST}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]
\begin{center}
  \includegraphics[width=\columnwidth]{figures/traintime/LSST10.pdf}}
\caption{Solid (dotted) blue line: Train time for models with varying
  size of the training set for LSST10 (nLSST10).  Train time roughly
  scales logarithmically with the train size, but the train time is
  also affected by model complexity.  Solid (dotted) red line: Best
  regularization parameter as a function of train size.  Note, LSST10
  requires more model complexity to exceed the performance of nLSST10
  (see blue solid and dotted lines in
  Figure~\ref{fig:trainsizeLSST}), and therefore requires more
  training time for continual increase in
  performance. }\label{fig:traintimeLSST10}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]
\begin{center}
  \includegraphics[width=\columnwidth]{figures/traintime/LSST-best.pdf}}
\caption{Same as Figure~\ref{fig:traintimeLSST10}, but for \edit{LSST-best}.
  Here, n\edit{LSST-best} requires more model complexity than \edit{LSST-best}.  Note, that
  \edit{LSST-best} and n\edit{LSST-best} have better seeing but reduced overall signal to
  noise than LSST10 and nLSST10.  This corresponds to better
  resolution, and therefore sharper edge features that prominently
  corespond to arcs.}\label{fig:traintimeLSST1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
